---
title: "Party Panel 17.1-pre2 Report"
author: "Greater Good (Gjalt-Jorn Peters)"
date: "`r format(Sys.time(), '%Y-%m-%d at %X');`"
output:
  html_document:
    toc: true
    theme: united
---

Party Panel 17.1-pre2 Report
============================

Introduction
------------

Party Panel is a Dutch panel study where determinants and beliefs underlying health behaviors in the Dutch nightlife are mapped. The third (2017) wave explored the determinants of visiting the first aid in case of problems.

This document is the report of the second pre-study, where members of the target population responded to a number of open questions, comparable to a belief elicitation procedure as recommended by Fishbein & Ajzen (2010). Put simply, they were asked about what they thought were the reasons people did, or did not, engage in the target behaviors selected in the first round.

```{r echo=FALSE, warning=FALSE}

########################################################################
### Packages
########################################################################

if (!require('userfriendlyscience', quietly = FALSE)) {
  stop("You need to have the userfriendlyscience package installed!");
}
safeRequire('here');
safeRequire('knitr');
safeRequire('pander');

########################################################################
### Settings
########################################################################

knitr::opts_chunk$set(echo=FALSE);
knitr::opts_chunk$set(cache=FALSE);
knitr::opts_chunk$set(comment=NA);

options(width = 160);
options(xtable.type = "html");
panderOptions('knitr.auto.asis', FALSE);
panderOptions('table.split.table', Inf);

########################################################################
### Set the variables with the paths
########################################################################

### Set the additional paths
outputPath <- here('preparation', 'pre2');
workingPath <- here('preparation', 'pre2');
dataPath <- here('preparation', 'pre2');
scriptPath <- here('preparation', 'pre2');

########################################################################
### Filenames
########################################################################

lsSurveyNumber <- 381842;
columnsToShow <- 10:35;
primaryVars <- c('earplugsUB', 'earplugsDB');

########################################################################
### Final automated settings and checks
########################################################################

dataFilename <- paste0('survey_', lsSurveyNumber, '_R_data_file.csv');
scriptFilename <- paste0('survey_', lsSurveyNumber, '_R_syntax_file.R');

allVars <- c("expertise", primaryVars, "recruitment");

########################################################################
### Read data
########################################################################

dat.raw <- importLimeSurveyData(datafile = file.path(dataPath, dataFilename),
                                scriptfile = file.path(scriptPath, scriptFilename),
                                encoding="UTF-8");

dat.cln <- dat.raw;

dat.cln$missings <-
  rowSums(is.na(dat.cln[, primaryVars]), na.rm=TRUE);

dat.cln <- dat.cln[dat.cln$missings == 0, ];

```

The raw dataset contained `r nrow(dat.raw);` rows and `r ncol(dat.raw);` columns. After removal of empty entries, `r nrow(dat.cln);` rows and `r ncol(dat.cln);` columns remained.

The full list of variablenames is `r vecTxt(names(dat.cln));`.

```{r echo=FALSE, results="asis"}

getLabel <- function(dat, varName) {
  return(attr(dat, 'variable.labels')[names(dat) == varName]);
}

showAnswersPerParticipant <- function(dat, varName, secondVarName=NULL) {
  if (length(na.omit(dat[, varName]))) {
    if (is.null(secondVarName)) {
      cat0("### ", varName, "\n",
           getLabel(dat, varName),  "\n\n",
           paste0(paste0("* id. ", dat[nchar(dat[, varName]) > 0 &
                                         !is.na(dat[, varName]), 'id'],
                         ": ", dat[nchar(dat[, varName]) > 0 &
                                     !is.na(dat[, varName]), varName]),
                  collapse="\n"), "\n\n");
    } else {
      cat0("### ", varName, "\n",
           getLabel(dat, varName),  "\n\n",
           getLabel(dat, secondVarName),  "\n\n",
           paste0(paste0("* id. ", dat[nchar(dat[, varName]) > 0 &
                                         !is.na(dat[, varName]), 'id'],
                         ": ", dat[nchar(dat[, varName]) > 0 &
                                     !is.na(dat[, varName]), varName],
                         " **-- justification --** ", dat[nchar(dat[, varName]) > 0 &
                                     !is.na(dat[, varName]), secondVarName]),
                  collapse="\n"), "\n\n");
    }
  } else {
    cat("###", varName, "\nThis variable has no data.\n\n");
  }
}

for (currentVar in allVars) {
  showAnswersPerParticipant(dat.cln, currentVar);
}

for (currentVar in 1:10) {
  showAnswersPerParticipant(dat.cln,
                            paste0("extraQuestions_vraag", currentVar),
                            paste0("extraQuestJustificat_vraag", currentVar));
}

```

