---
title: "Party Panel 16.2-pre2 Report"
author: "Greater Good (Gjalt-Jorn Peters)"
date: "`r format(Sys.time(), '%d %b %Y at %H:%M:%S');`"
output:
  html_document:
    toc: true
    #toc_float: true
    toc_depth: 5
    theme: united
    css: "B:\\Data\\research\\party panel\\15.1\\results - analysis scripts\\party panel reports.css"
---

Introduction
------------

Party Panel is a Dutch panel study where determinants and beliefs underlying health behaviors in the Dutch nightlife are mapped. The second wave started on the first of October 2016 and explored behavior related to hearing damage.

This document is the report of the first pre-study, where members of expert organisations responded to a number of open questions about which exact behavior they thought should be targeted in PP16.2.

```{r echo=FALSE, warning=FALSE, message=FALSE }

### Set basic configuration variables
if (!exists('ppWave')) ppWave <- '16.2';
if (!exists('ppReport')) ppReport <- 'pre1';
if (!exists('basePath')) basePath <- 'B:/Data/research/party panel';
if (!exists('surveyid')) surveyid <- '987793';
if (!exists('regularVars')) regularVars <- c('personalInfo_name',
                                             'personalInfo_role',
                                             'personalInfo_organisation',
                                             'personalInfo_email',
                                             'suggestion',
                                             'justification',
                                             'recruitment');
if (!exists('loopVars')) loopVars <- c('extraQuestions_vraag',
                                       'extraQuestJustificat_vraag');
if (!exists('loopNr')) loopNr <- 10;
if (!exists('requiredQuestions')) requiredQuestions <- c('suggestion');

### Automatically generate further configuration variables
dataPath <- file.path(basePath, ppWave, 'preparation', ppReport, 'data');
dataFilename <- paste0('survey_', surveyid, '_R_data_file.csv');
scriptFilename <- paste0('survey_', surveyid, '_R_syntax_file.R');

  require('pander', quietly=TRUE);
  require('xtable', quietly=TRUE);

  knitr::opts_chunk$set(echo=FALSE);
  knitr::opts_chunk$set(cache=FALSE);
  knitr::opts_chunk$set(comment=NA);

  options(width = 160);
  options(xtable.type = "html");
  panderOptions('knitr.auto.asis', FALSE)
  panderOptions('table.split.table', Inf)

### Check for required package
if (!require('userfriendlyscience')) {
  stop("You need to have the userfriendlyscience package installed!");
}

### Make object for Party Panel data
if (!exists('ppDat')) ppDat <- list();
if (!(ppWave %in% names(ppDat))) ppDat[[ppWave]] <- list();

### Read data
ppDat[[ppWave]][[ppReport]] <- list();
  ppDat[[ppWave]][[ppReport]]$raw <-
    importLimeSurveyData(datafile = file.path(dataPath, dataFilename),
                         scriptfile = file.path(dataPath, scriptFilename));
ppDat[[ppWave]][[ppReport]]$cln <- ppDat[[ppWave]][[ppReport]]$raw;

### Count missing values
if (length(requiredQuestions) > 1) {
  ppDat[[ppWave]][[ppReport]]$cln$missings <-
    rowSums(is.na(ppDat[[ppWave]][[ppReport]]$cln[, requiredQuestions]), na.rm=TRUE);
} else {
  ppDat[[ppWave]][[ppReport]]$cln$missings <-
    as.numeric(is.na(ppDat[[ppWave]][[ppReport]]$cln[, requiredQuestions]));
}

### Remove rows with missing values
ppDat[[ppWave]][[ppReport]]$cln <-
  ppDat[[ppWave]][[ppReport]]$cln[ppDat[[ppWave]][[ppReport]]$cln$missings == 0, ];

```

The raw dataset contained `r nrow(ppDat[[ppWave]][[ppReport]]$raw);` rows and `r ncol(ppDat[[ppWave]][[ppReport]]$raw);` columns. After removal of empty entries, `r nrow(ppDat[[ppWave]][[ppReport]]$cln);` rows and `r ncol(ppDat[[ppWave]][[ppReport]]$cln);` columns remained.

The full list of variablenames is `r vecTxt(names(ppDat[[ppWave]][[ppReport]]$cln));`.

```{r echo=FALSE, results="asis"}

getLabel <- function(dat, varName) {
  return(attr(dat, 'variable.labels')[names(dat) == varName]);
}

showAnswersPerParticipant <- function(dat, varName, secondVarName=NULL) {
  if (length(na.omit(dat[, varName]))) {
    if (is.null(secondVarName)) {
      cat0("### ", varName, "\n",
           getLabel(dat, varName),  "\n\n",
           paste0(paste0("* id. ", dat[nchar(dat[, varName]) > 0 &
                                         !is.na(dat[, varName]), 'id'],
                         ": ", dat[nchar(dat[, varName]) > 0 &
                                     !is.na(dat[, varName]), varName]),
                  collapse="\n"), "\n\n");
    } else {
      cat0("### ", varName, "\n",
           getLabel(dat, varName),  "\n\n",
           getLabel(dat, secondVarName),  "\n\n",
           paste0(paste0("* id. ", dat[nchar(dat[, varName]) > 0 &
                                         !is.na(dat[, varName]), 'id'],
                         ": ", dat[nchar(dat[, varName]) > 0 &
                                     !is.na(dat[, varName]), varName],
                         " **-- JUSTIFICATION --** ", dat[nchar(dat[, varName]) > 0 &
                                     !is.na(dat[, varName]), secondVarName]),
                  collapse="\n"), "\n\n");
    }
  } else {
    cat("###", varName, "\nThis variable has no data.\n\n");
  }
}

for (currentVar in regularVars) {
  showAnswersPerParticipant(ppDat[[ppWave]][[ppReport]]$cln, currentVar);
}

for (currentVar in 1:10) {
  showAnswersPerParticipant(ppDat[[ppWave]][[ppReport]]$cln,
                            paste0(loopVars[1], currentVar),
                            paste0(loopVars[2], currentVar));
}

```


